---
title: "Educational Measures Downloaded Data Inventory"
author: "Prestige Services"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document:
        includes:
          in_header: header.tex
  word_document:
        reference_docx: headingthree.docx
        highlight: tango
        df_print: tibble
        fontsize: 12pt
header-includes: \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[CO,CE]{} \fancyfoot[CO,CE]{
  Downloaded Data Inventory for Educational Measures} \fancyfoot[LE,RO]{\thepage}
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(kableExtra)

DataRoot <- "data/agentExports"

source("awsADS_functions.R")

knitr::opts_chunk$set(echo = FALSE)
```

# AWS Data Inventory

The purpose of this report is to provide a high-level summary of the records collected to date.  We will refresh this report periodically to make sure we are making progress toward our goal of getting about 14 days worth of performance data for each system.  Refer to the the table titled **Performance Time Spans (Days) by Hostname** and the **Perf.Days** column.


```{r Inv2, results = 'asis', fig.cap = "Performance Time Spans (Days) Days by Hostname"}

compInventory <- getCompInventory(DataRoot)

# Calculate the number of Days Performance for each server (hostName)

host_perf_time <- compInventory %>% 
  group_by(hostName) %>% 
  summarize(First = ymd_hms(min(timestamp)),
            Last = ymd_hms(max(timestamp)), 
            Perf.Days = difftime(Last, First, units = "days"))
  
knitr::kable(host_perf_time, digits = 2, format = "markdown", caption = "Performance Days by Hostname")
  
#     column_spec(4, background = "yellow")  
# knitr::kable(host_perf_time, digits = 2, format = "latex", caption = "Performance Days by Hostname") %>%
#   kable_styling(bootstrap_options = "basic", full_width = FALSE, latex_options = "basic", 
#                 position = "hold_position", font_size = NULL) %>%
#     column_spec(4, background = "yellow")
```


\clearpage

### List Agent IDs in Current Data Store

The agent IDs are the unique identifiers of the AWS ADS agents installed within the customer's data center.  In the case of VMware hypervisor VMs, the agent ID is the identity of the OVA appliance installed. If additional performance metrics are required for a VM or the customer has a non-virtualized server, the agent ID is the identity of the actual agent installed on the server or VM.

Following are the Agent IDs found in the data store containing exported data from the AWS Migration Hub.  The Agent IDs will be used to identify which environment the data pertain to.

```{r}
agentIDs <- getAgentIDs(root = DataRoot)  # this list is required at many places in subsequent blk
collected <- getHostCollection(DataRoot)

knitr::kable(collected, format = "latex") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
   row_spec(0,angle = -45) 
```

There are `r length(agentIDs)` Agent IDs.  See the list of these immediately above.

\clearpage


### AWS/ADS Records per Collection Type by Agent ID


```{r Inv1, results = 'asis'}
resList <-   map(agentIDs, ~ getResults(DataRoot,. ))
osList  <-   map(agentIDs, ~ getosInfo(DataRoot,. ))
prList  <-   map(agentIDs, ~ getPerf(DataRoot,. ))
nwList  <-   map(agentIDs, ~ getNetworkInterface(DataRoot,. ))
dpList  <-   map(agentIDs, ~ getDestProcConn(DataRoot,. ))
spList  <-   map(agentIDs, ~ getSrcProcConn(DataRoot,. ))
pList   <-   map(agentIDs, ~ getProcess(DataRoot,. ))



inventory <- tibble(
  Number           = seq(1:length(agentIDs)),
  Hostname         = collected$Hostname, 
  Results          = map_int(resList, ~ nrow(.)),
  OSInfo           = map_int(osList, ~ nrow(.)),
  Performance      = map_int(prList, ~ nrow(.)),
  NetworkInterface = map_int(nwList, ~ nrow(.)),
  DstProcessCon    = map_int(dpList, ~ nrow(.)),
  SrcProcessCon    = map_int(spList, ~ nrow(.)),
  Processes        = map_int(pList,  ~ nrow(.))
  )
  
knitr::kable(inventory, format = "latex", 
             cap="AWS/ADS Records per Collection Type by Agent ID") %>%
   kable_styling(bootstrap_options = c("striped"), full_width = F) %>%
   column_spec(2, width = "10em", background = "yellow") %>%
   row_spec(0,angle = -45)
```




```{r ExportData, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
### Export Performance and OS Information Data to Excel Spreadsheet

### Export Performance and OS Information Data to Excel Workbook
Sys.setenv("R_ZIPCMD" = "C:/Rtools/bin/zip.exe")
library(openxlsx)

# Create Nested file from compInventory
comp_n <- compInventory %>%
  mutate(Host = hostName) %>%
  group_by(Host) %>%
      nest()

## Create Excel Workbook with each hostName (agentId) on a separate tab.
fn <- paste("EM_performance_","(",as.Date(Sys.time()),").xlsx", sep = "")

if (file.exists(fn)) file.remove(fn)  # to ensure we are writing a brand new file.

## Create workbook and add empty worksheets
wb <- createWorkbook(fn)
walk(comp_n$Host,~ addWorksheet(wb, strtrim(.,31)))

# Write the data to Worksheets
walk2(comp_n$data, comp_n$Host,~ writeData(wb, strtrim(.y,31), .x))

# Save Workbook
saveWorkbook(wb, fn, overwrite = TRUE)

```

Workbook created: **`r fn`** with **`r length(sheets(wb))`** worksheets (tabs).


**Run Date: **"`r format(Sys.time(), '%d %B %Y')`"

