---
title: "Educational Measures Host Performance Statistics"
author: "Prestige Services"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  pdf_document: 
        includes:
          in_header: header.tex
  word_document:
        reference_docx: headingthree.docx
        highlight: tango
        df_print: tibble
        fontsize: 12pt
header-includes: \usepackage{fancyhdr} \pagestyle{fancy} \fancyhead[CO,CE]{} \fancyfoot[CO,CE]{
  Host Performance Statistics for Educational Measures} \fancyfoot[LE,RO]{\thepage}

---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(kableExtra)
library(rlang)
library(broom)


source("awsADS_functions.R")

knitr::opts_chunk$set(echo = FALSE)
```


# Host Performance Statistics

The purpose of this report is to provide statistics of system performance in tabular and graphical form.  The data are collected by agents installed on each server.

## Reports

This document will detail four areas of concern:

* CPU Utilization 
* Memory Utilization
* Storage Utilization
* NetworkUtilization

In each of these areas, we will display tabular and graphical data as tools to make recommendations for resizing your current deployments.

### List Agent IDs in Current Data Store

The agent IDs are the unique identifiers of the AWS ADS agents installed within the customer's data center.  In the case of VMware hypervisor VMs, the agent ID is the identity of the OVA appliance installed. If additional performance metrics are required for a VM or the customer has a non-virtualized server, the agent ID is the identity of the actual agent installed on the server or VM.

Following are the Agent IDs found in the data store containing exported data from the AWS Migration Hub.  The Agent IDs will be used to identify which environment the data pertain to.

```{r}


DataRoot <- "data/agentExports"
agentIDs <- getAgentIDs(root = DataRoot)

compInventory <- getCompInventory(DataRoot)
collection <- getHostCollection((DataRoot))
coll <- collection %>%
  select(-1) %>%
  arrange(Hostname)
knitr::kable(coll)
```

There are `r length(agentIDs)` Agent IDs.  See the list of these immediately above.

## Data Inventory

The purpose of this report is to provide a high-level summary of the records collected to date.  We will refresh this report periodically to make sure we are making progress toward our goal of getting about 14 days worth of performance data for each system.  Refer to the the table titled **Performance Time Spans (Days) by Hostname** and the **Perf.Days** column.

```{r Inv2, results = 'asis', fig.cap = "Performance Time Spans (Days) Days by Hostname"}

compInventory <- getCompInventory(DataRoot)

# Calculate the number of Days Performance for each server (hostName)

host_perf_time <- compInventory %>% 
  group_by(hostName) %>% 
  summarize(First = ymd_hms(min(timestamp)),
            Last = ymd_hms(max(timestamp)), 
            Perf.Days = difftime(Last, First, units = "days"))
  
knitr::kable(host_perf_time, digits = 2, format = "markdown", caption = "Performance Days by Hostname")
  
#     column_spec(4, background = "yellow")  
# knitr::kable(host_perf_time, digits = 2, format = "latex", caption = "Performance Days by Hostname") %>%
#   kable_styling(bootstrap_options = "basic", full_width = FALSE, latex_options = "basic", 
#                 position = "hold_position", font_size = NULL) %>%
#     column_spec(4, background = "yellow")
```

\clearpage

## Names of Performance and OS Fields


```{r Fields, results = 'asis'}

knitr::kable(names(compInventory), col.names = c("Performance Fields"), caption = "Fields Avalilable in Performance Data")

```

\clearpage

## CPU Utilization

```{r CPU, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

df <- compInventory %>% arrange(hostName)
cpu_sizing <- getCPUs(df)
knitr::kable(cpu_sizing,digits = 2, format = "latex") %>%
  add_header_above(c(" " = 1, "CPU Utilization (Percent)" = 6, "Cores" = 3))

```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(scales)
library(data.table)
ce <- tibble(
  Host = cpu_sizing$Host,
  Mean = cpu_sizing$Mean,
  P95  = cpu_sizing$P95,
  Max  = cpu_sizing$Max
)
legend_title <- "Statistic"

ce <- arrange(ce, Host)
mce <- melt(ce,id.vars = "Host")
ggplot(mce, aes(x = Host, y = value, fill = variable)) + 
  geom_bar(position = "dodge", stat = "identity") + ylab("Percent CPU Utilization") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  scale_fill_manual(legend_title, values = c("red", "blue", "green"))

```

\clearpage

## Memory Utilization

```{r}

mem_sizing <- getMEMs(df)
knitr::kable(arrange(mem_sizing, Host), digits = 2,  format = "latex") %>%
  add_header_above(c(" " = 1, "RAM Megabytes Free" = 5, "Real" = 1, " " = 1, "Percent" = 1))
```

```{r}
me <- tibble(
  Host = mem_sizing$Host,
  Mean = mem_sizing$Mean,
  Max  = mem_sizing$Max,
  RAM  = mem_sizing$RAM.MB
)
me <- arrange(me, Host)
mme <- melt(me,id.vars = "Host")
ggplot(mme, aes(x = Host, y = value, fill = variable)) + 
  geom_bar(position = "dodge", stat = "identity") + ylab("RAM Utilization (MB)") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  scale_fill_manual(legend_title, values = c("red", "blue", "green"))

```

\clearpage

## Host Performance Statistics

```{r , fig.height= 4.0,reults = "asis", comment = "", echo = FALSE}
comp_n <- compInventory %>% arrange(hostName) %>% group_by(agentId) %>% nest()

Host = fixHostnames(map_chr(agentIDs, ~ subset(df,agentId == .x)$hostName[1]))
Data <-  map(agentIDs, ~ subset(df,agentId == .x))


for (i in 1:length(comp_n$agentId)) {
  
# -------------------------------------------------------------------------------------  PAGE 1
   
####################################################################################### CPUUSAGPCT
  par(mfrow = c(2,1))
  hdr <- paste("Host: ", Host[i]," Metric: CpuUsagePct", sep = "")
  p <- ggplot(Data[[i]], aes(x = timestamp, y = CpuUsagePct)) + geom_line() + 
   ggtitle( label = hdr) + xlab("Date") + ylab("CPU Utilization Percent")
  print(p)

###################################################################################### MEMUSAGEPCT
   hdr <- paste("Host: ", Host[i]," Metric: MemUsagePct", sep = "")
   Data[[i]]$MemUsagePct <- (Data[[i]]$RAM.MB - Data[[i]]$freeRAM.MB) /  Data[[i]]$RAM.MB * 100
   p <- ggplot(Data[[i]], aes(x = timestamp, y = MemUsagePct)) + geom_line() + 
      ggtitle( label = hdr) + xlab("Date") + ylab("Memory Utilization Percent")
   print(p)  

  # ------------------------------------------------------------------------------------- PAGE 2
   par(mfrow = c(2,1))
   ####################################################################################### DISKUTIL
  # hdr <- paste("Host: ", Host[i]," Metric: DskUtilPct", sep = "")
  # Data[[i]]$ DskUtilPct <- (Data[[i]]$DiskSize.GB - Data[[i]]$DiskFreeSize.GB) /  Data[[i]]$DiskSize.GB * 100
  # p <- ggplot(Data[[i]], aes(x = timestamp, y = DskUtilPct)) + geom_line() + 
  #  ggtitle( label = hdr) + xlab("Date") + ylab("Disk Utilization Percent")
  # print(p)

  ####################################################################################### DISK READS + WRITES
   hdr <- paste("Host: ", Host[i]," Metric: DskBytes Written and Read", sep = "")
   dskDat <- Data[[i]] %>%
     select(c("timestamp","DiskBytesReadPS", "DiskBytesWrittenPS"))
   mDskDat <- melt(dskDat, id = "timestamp")
   p <- ggplot(mDskDat, aes(x = timestamp, y = value, color = variable)) + geom_line() + 
      ggtitle( label = hdr) + xlab("Date") + ylab("Disk Read and Write Rates (Bytes per second)") +
      scale_fill_manual("Metric", values = c("red", "blue"))

   print(p) 
   
   
# ------------------------------------------------------------------------------------- PAGE 3

      
####################################################################################### NETWORK READS + WRITES
   hdr <- paste("Host: ", Host[i]," Metric: NetworkBytes Written and Read", sep = "")
   dskDat <- Data[[i]] %>%
     select(c("timestamp","NetworkBytesReadPS", "NetworkBytesWrittenPS"))
   mDskDat <- melt(dskDat, id = "timestamp")
   p <- ggplot(mDskDat, aes(x = timestamp, y = value, color = variable)) + geom_line() + 
      ggtitle( label = hdr) + xlab("Date") + ylab("Network Read and Write Rates (Bytes per second)") +
      scale_fill_manual("Metric", values = c("red", "blue"))
   print(p) 
   #cat("\\newpage")
}
```


**Run Date: **"`r format(Sys.time(), '%d %B %Y')`"